---
title: "HW2_631"
author: "Prashan Welipitiya"
date: "2/13/2020"
output: pdf_document
---
# Exercise 1

a.
```{r}
data1 = read.table("http://www.stat.umn.edu/~gary/book/fcdae.data/ex3.1",header=TRUE)
# data1

mu = mean(data1$y)
mu1 = mean(data1[which(data1$diet==1),]$y)
mu2 = mean(data1[which(data1$diet==2),]$y)
mu3 = mean(data1[which(data1$diet==3),]$y)
mu4 = mean(data1[which(data1$diet==4),]$y)
a1 = mu1 - mu
a2 = mu2 - mu
a3 = mu3 - mu
a4 = mu4 - mu

# Overall mean
mu

# treatment effects
a1
a2
a3
a4

```
b. 
$H_0 : \alpha_1 = \alpha_2 = \alpha_3 = \alpha_4 = 0$  
$H_A : \alpha_i \neq \alpha_j$ for at least for at least one pair (i,j). 
```{r}
data1$fdiet = as.factor(data1$diet)
#  head(data1)
# summary(data1)
full.model<-aov(y~fdiet,data=data1)
anova(full.model)
```

Because the p value is less than 0.05 and the F value is greater than 1, we reject the null hypothesis and conclude that the data supports the claim that the group means are different. 

# Exercise 3.
```{r}
data2 = read.table("http://www.stat.umn.edu/~gary/book/fcdae.data/ex3.3",header=TRUE)
# data2
```
$H_0 : \alpha_1 = \alpha_2 = \alpha_3 = \alpha_4 = 0$  
$H_A : \alpha_i \neq \alpha_j$ for at least for at least one pair (i,j). 

```{r}
data2$ftrt = as.factor(data2$trt)
# head(data1)
# summary(data1)
full.model<-aov(mc~ftrt,data=data2)
anova(full.model)
```

Both the F value is close to 1 and the p value is greater than 0.05 so we fail to reject the null hypothesis. 
